Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-12-18 WSSSPE4_report/WSSSPE4_paper.tex
minor grammer - finished reviewed Anshu's changes (Thanks again Anshu!)

Anyone can join this group or obtain more information about it, by sending an email to the verifying best practices \& metrics for sustainable research software group: <wssspe4-verify-best-practices@googlegroups.com>.

>>>>

Anyone can join this group or obtain more information about it by sending an email to the verifying best practices \& metrics for sustainable research software group: <wssspe4-verify-best-practices@googlegroups.com>.
